Hourly Assimilation of Different Sources of Observations Including Satellite Radiances in a  Mesoscale Convective System Case During RELAMPAGO campaign

### 2022-08-23 analysis/paper/paper_ana_20181122.Rmd
Actualiza al nuevo elsevier

# layout: authoryear,preprint,review,12pt
layout: final,5p,times,twocolumn,authoryear

@@

bibliography: [paperANA.bib, packages.bib, era.bib]
csl: elsevier-harvard.csl

@@

header-includes: 

@@

```{r table-rad}
fread(here("analysis/data/derived_data/tables/tabla_radianzas.csv")) %>% 
  .[, ":="(sensor = toupper(sensor),
           plataforma = toupper(plataforma),
           prop = paste0(prop, " \\", "%"))] %>% 
  .[order(.[,'sensor']), ] %>% 
  .[] %>% 
  kbl(booktabs = TRUE,
      escape = FALSE,
      col.names = linebreak(c("Sensor", "Platform", "Assimilated\nchannels", "Percentage\nover total")),
      caption = "List of the available sensors over several platforms, the number of accepted channels for the assimilation, and the percentage of assimilated observations calculated over all radiance observations and all cycles.") %>% 
  kable_styling(font_size = 7) %>% 
  collapse_rows(1, valign = "top") %>% 
  kable_classic_2(full_width = TRUE)
```

@@

IOP 7 (Figures \@ref(fig:soundings)a-d) provides a good characterization of the pre-convective environment during the first day of our experiments. The area where the observations were taken was characterized by mostly clear skies and a low-level northerly flow associated with warm and moist advection. In general, the experiments show a similar RMSE and bias for all the variables. AWS observations were able to reduce the RMSE for temperature and dew point temperature in the PBL and reduce a small dry bias. However, in this region (Figure \@ref(fig:domain)b) and for this period, AWS increments (Figure \@ref(fig:UV-diff)d) degradated the zonal wind between 7 and 12 km increasing the bias and RMSE (Figure \@ref(fig:soundings)c).

>>>>

#layout: authoryear,preprint,review,12pt
# layout: final,5p,times,twocolumn,authoryear
classoption: preprint, 3p, authoryear

@@

bibliography: "paperANA.bib,packages.bib,era.bib"
# csl: elsevier-harvard.csl

@@

# header-includes: 

@@

```{r table-rad}
fread(here("analysis/data/derived_data/tables/tabla_radianzas.csv")) %>%
  .[, ":="(sensor = toupper(sensor),
           plataforma = toupper(plataforma),
           prop = paste0(prop, " ", "%"))] %>%
  .[order(.[,'sensor']), ] %>%
  .[] %>%
  kbl(booktabs = TRUE,
      escape = TRUE,
      col.names = linebreak(c("Sensor", "Platform", "Assimilated channels", "Percentage over total")),
      caption = "List of the available sensors over several platforms, the number of accepted channels for the assimilation, and the percentage of assimilated observations calculated over all radiance observations and all cycles.") %>%
  kable_styling(font_size = 7) %>%
  collapse_rows(1, valign = "top") %>%
  kable_classic_2(full_width = TRUE)
```

@@

IOP 7 (Figures \@ref(fig:soundings)a-d) provides a good characterization of the pre-convective environment during the first day of our experiments. The area where the observations were taken was characterized by mostly clear skies and a low-level northerly flow associated with warm and moist advection. In general, the experiments show a similar RMSE and bias for all the variables. AWS observations were able to reduce the RMSE for temperature and dew point temperature in the PBL and reduce a small dry bias. However, in this region (Figure \@ref(fig:dominio)b) and for this period, AWS increments (Figure \@ref(fig:UV-diff)d) degradated the zonal wind between 7 and 12 km increasing the bias and RMSE (Figure \@ref(fig:soundings)c).
